maxent model avec xvalidation (year-based test training)

### 2019-06-06 src/stack_test.Rmd
messing with land masses

>>>>

------------------------

# trim layer by polygon

C:\Users\bunny\Documents\GitHub\Chapter_1\output\maxent\predictions\jun\avg_cloglog_147.406.asc
C:\Users\bunny\Documents\GitHub\Chapter_1\output\bio\minimum_convex_poly\mcp_capelin_100_poly.shp
C:\Users\bunny\Documents\GitHub\Chapter_1\output\env\aea.tif

```{r}
testras <- raster("../output/maxent/predictions/jun/avg_cloglog_147.406.asc")
mcp <- readOGR("../output/bio/minimum_convex_poly/mcp_capelin_100_poly.shp") 
aea <- raster("../output/env/aea.tif")
plot(testras)
plot(mcp)
class(mcp)
rr <- mask(testras, mcp)
plot(rr); plot(mcp, add = TRUE)
plot(testras); plot(mcp, add = TRUE)
plot(rr);plot(testras)
```

# add landmass

```{r}
us <- getData("GADM", country="USA", level=0)
plot(us)
class(us)
projection(testras) <- CRS(aea)

us <- spTransform(us, CRS(projection(aea)))

crs(testras) <- aea

rr <- mask(aea, us)
plot(us)

a <- plot(testras); plot(us, add = TRUE)
